---
title: "HW 1 P8105"
author: "Michelle Poimboeuf"
date: 2020-09-17
output: github_document
---

This is my solution to HW1

```{r}
library(tidyverse)
```

## Problem 1

Create a dataframe with the specified elements.

```{r}
prob1_df = 
tibble(
  samp = rnorm(10),
  samp_gt_0 = samp > 0, 
  char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod","mod", "high", "high", "high"))
)
```

Take the mean of each variable in my data frame. 

```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```
I can take the mean of the numeric and logical vectors, but not the factor or the character vectors. 
This makes some sense as numbers have means. It is a bit confusing as to why you would be able to take the
mean of the logical vector, when you wouldn't be able to take it of the factor or character vectors. I see that R will code things in a way that does not necessarily make sense. 

```{r}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

Above, adding the as.numeric code to the beginning of the chunk explicitly performs the action that R was performing behind the scenes in the last code chunk. It shows the steps to coding the vectors as numeric and helps explain why R thinks it can take the mean of certain vectors. 

Second Code Chunk for Problem 1:

```{r}
as.numeric(pull(prob1_df, samp_gt_0))*pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0))*pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0))*pull(prob1_df, samp)
```


